Privacy-Respecting Type Error Telemetry at Scale

### 2023-09-30 programming23/paper.tex
sec 5

Luau has an efficient type checker that can
analyze thousands of lines of code~(\cref{t:codebase-size}).
But, few sessions use type analysis directly and the data presents little
evidence that doing so would improve creators' quality of life.
We conjecture that Luau needs further tailoring to match
common idioms in Roblox scripts.
Discovering these idioms is a question for future work~(\cref{s:conclusion}).

@@

Third, session-based data has limitations.
A creator who closes and reopens Roblox Studio every day has
a much higher chance of generating telemetry than one who
leaves Studio open all week.
We have no way to reliably check whether multiple sessions are
reporting on the same codebase.
Sessions may end abruptly, for instance because of machine reboot,
instead of ending when the creator was finished editing code.

>>>>

Luau has an efficient type checker that can
analyze thousands of lines of code~(\cref{t:codebase-size}) quickly
enough to be used on-the-fly in an IDE.
But, few sessions use type analysis directly and the data presents little
evidence that doing so would improve creators' quality of life.
We conjecture that Luau needs further tailoring to match
common idioms in Roblox scripts.
Discovering these idioms is a question for future work~(\cref{s:conclusion}).

@@

Third, session-based data has limitations.
A creator who closes and reopens Roblox Studio every day has
a much higher chance of generating telemetry than one who
leaves Studio open all week.
We have no way to reliably check whether multiple sessions are
reporting on the same codebase.
Sessions may end abruptly, e.g., because of machine reboot,
instead of ending when the creator was done editing code.
